Data-driven approaches to identifying knowledge gaps in marine invertebrate biodiversity

### 2017-05-31 manuscript.Rmd
write some words

We combined `r nrow(idigbio_records)` museum records for marine invertebrates collected in the EEZ waters of the continental US representing `r length(unique(tolower(idigbio_records[["data.dwc:phylum"]])))` phyla and `r length(unique(idigbio_records$worms_valid_name))` species. Most samples were collected on the continental shelf (Fig. 1). For the East coast, species richness is the highest in South Florida but it is relatively uniform along the coastline. For the West coast, the Salish Sea, the Bay Area, and Southern California have the highest richness (Fig. 2).

```{r map-diversity-sampling, fig.cap='Spatial distribution of the number of samples (A) and species richness (B) for marine invertebrates based on specimen data available from iDigBio within the limits of the Exclusive Economic Zone for the contiental USA.'}
knitr::include_graphics("figures/map_diversity_sampling.pdf")
```

Based on these data, there is no evidence of a diversity gradient.

>>>>

We combined `r nrow(idigbio_records)` museum records for marine invertebrates collected in the EEZ waters of the continental US representing `r length(unique(tolower(idigbio_records[["data.dwc:phylum"]])))` phyla and `r length(unique(idigbio_records$worms_valid_name))` species. Most samples were collected on the continental shelf (Fig. \@ref(fig:map-diversity-sampling)A). For the East coast, species richness is the highest in South Florida but it is relatively uniform along the coastline. For the West coast, the Salish Sea, the Bay Area, and Southern California have the highest richness (Fig. \@ref(fig:map-diversity-sampling)B).

```{r map-diversity-sampling, fig.cap='Spatial distribution of the number of samples (A) and species richness (B) for marine invertebrates based on specimen data available from iDigBio within the limits of the Exclusive Economic Zone for the contiental USA. (\\#fig:map-diversity-sampling)'}
knitr::include_graphics("figures/map_diversity_sampling.pdf")
```

These patterns of spatial distribution of the species richness is strongly confounded by the sampling. When investigating the relation between the number of samples and the number of species for each cell of the map (\@ref(fig:correlation-sampling)), we can see that until reaching about 100 records per 0.5° there is little redundancy in the sampled species.

```{r correlation-sampling, fig.cap='Relation between number of records and number of species for each cell of the map used in \\@ref(fig:map-diversity-sampling)'}
knitr::include_graphics("figures/plot_sampling_effort.pdf")
```
